A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-02 sections/Related.tex
to match the screenshot
Ningning

\jimmy{Let arguments go first by Ningning}
In a more recent work, \citet{xie2018letarguments} proposed a variant of
bidirectional type inference system where type information flows from arguments to
functions with an additional \emph{application} mode,
which allows more higher-order typed programs to be inferred without additional annotations.
Following the new mode, the let-generalization of the Hindley-Milner system
is well supported as a syntactic sugar.
Unfortunately, no formal proofs are given for the correctness of its algorithmic system.

@@

\paragraph{Mechanical Formalization of Polymorphic Subtyping}
In all previous work on type inference for higher-ranked polymorphism
(predicative and impredicative) discussed above, proofs and
metatheory are manual. The only partial effort on mechanizing aspects of type inference
for higher-ranked types is
the Abella formalization of \emph{polymorphic subtyping} by \citet{itp2018}.
The judgment form of worklist $\Gm \vdash \Omega$ used in the formalization simplifies
the propagation of existential variable instantiations.
However, the approach has two main drawbacks:
it does not collect unused variable declarations effectively;
and the simple form of judgment cannot handle inference modes, which output types.
The new worklist introduced in this paper inherits the simplicity of propagating instantiations,
but overcomes both of the issues by mixing judgments with declarations
and using the continuation-passing-style judgment chains. Furthermore,
we formalize the complete bidirectional type system by
\citet{dunfield2013complete}, whereas Zhao et al. only formalize
the subtyping relation.

>>>>

In a more recent work, \citet{xie2018letarguments} proposed a variant of a
bidirectional type inference system for a predicative system with higher-ranked types.
Type information flows from arguments to
functions with an additional \emph{application} mode. This variant 
allows more higher-order typed programs to be inferred without additional annotations.
Following the new mode, the let-generalization of the Hindley-Milner system
is well supported as a syntactic sugar. The formalization includes some
mechanized proofs for the declarative type system, but all proofs regarding
the algorithmic type system are manual.

@@

\paragraph{Mechanical Formalization of Polymorphic Subtyping}
In all previous work on type inference for higher-ranked polymorphism
(predicative and impredicative) discussed above, proofs and
metatheory for the algorithmic aspects are manual. The only partial effort on mechanizing algorithmic
aspects of type inference
for higher-ranked types is
the Abella formalization of \emph{polymorphic subtyping} by \citet{itp2018}.
The judgment form of worklist $\Gm \vdash \Omega$ used in the formalization simplifies
the propagation of existential variable instantiations.
However, the approach has two main drawbacks:
it does not collect unused variable declarations effectively;
and the simple form of judgment cannot handle inference modes, which output types.
The new worklist introduced in this paper inherits the simplicity of propagating instantiations,
but overcomes both of the issues by mixing judgments with declarations
and using the continuation-passing-style judgment chains. Furthermore,
we formalize the complete bidirectional type system by
\citet{dunfield2013complete}, whereas Zhao et al. only formalize
the subtyping relation.
